Patient-Specific Neural Field Modeling from Mirco-Electrode Data

### 2010-07-20 ltx/data_paper/DataPaper.tex
commiting for merge

@@

\subsection{Estimating Support For Connectivity Kernel}
The support for the connectivity kernel can be inferred...

@@

\subsection{state-space model}
The state space model is given by

>>>>

To relate the model to the data the electrodes are also modelled. The electrodes have a pick-up range (for LFPs) of approximately 400~$\mu$m. Therefore, we model the electrodes as a spatial convolution of a Gaussian shaped sensor kernel (using a width parameters of 400~$\mu$m) with the neural field. The observation equation is
\begin{equation}
    \label{eq:ObservationEquation}
	\mathbf{y}_t =
	\int_{\Omega}{
	    m\left(\mathbf{r}_n-\mathbf{r}'\right)v_t\left(\mathbf{r}'\right)
	\textrm{d}\mathbf{r}'} + 
	\boldsymbol{\varepsilon}_t, 
\end{equation}
where $\mathbf{r}_n$ defines the location of the sensors in the field, $n=1,...,N$ indexes the sensors and $\boldsymbol{\varepsilon}_t \sim \mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$. $\mathcal{N}\left(0,\boldsymbol{\Sigma}_{\varepsilon}\right)$ denotes the multivariate normal distribution with mean zero and covariance matrix $\boldsymbol{\Sigma}_{\varepsilon}$. The sensor kernel, $m(\mathbf{r}-\mathbf{r}')$, is defined by 
\begin{equation}
	m\left(\mathbf{r}-\mathbf{r}'\right) = \exp{\left(-\frac{(\mathbf{r}-\mathbf{r}')^\top(\mathbf{r}-\mathbf{r}')}{\sigma_m^2}\right)},
\end{equation}
where $\sigma_m$ sets the sensor width. Under the assumption that the basis function decomposition is accurate, the observation equation of the reduced model is found by substituting equation~\ref{DefFieldDecomp} into~\ref{eq:ObservationEquation} giving
\begin{equation}\label{eq:ReducedObservationEquation}
	\mathbf{y}_t = \int_{\Omega}{m\left(\mathbf{r}_n-\mathbf{r}'\right)\boldsymbol{\phi}^{\top}\left(\mathbf{r'}\right) \mathbf{x}_t\textrm{d}\mathbf{r}'} + \boldsymbol{\varepsilon}_t. 
\end{equation}
The observation equation is linear with respect to the state and can be written in the more compact form
\begin{equation}\label{ObservationEquation} 
	\mathbf{y}_t = \mathbf{C}\mathbf{x}_t + \boldsymbol{\varepsilon}_t,
\end{equation}
where the observation matrix is 
\begin{equation}
	\mathbf{C} = \left[
	\begin{array}{{ccc}} 
		c_{1,1} & \dots & c_{1,L} \\
		\vdots & \ddots & \vdots \\
		c_{N,1} & \dots & c_{N,L} 
	\end{array}
	\right] 
\end{equation}
and 
\begin{equation}
	c_{i,j} = \int_{\Omega}m(\mathbf{r}_i - \mathbf{r}')\boldsymbol{\phi}_j(\mathbf{r}')\textrm{d}\mathbf{r}'. 
\end{equation}

@@

\subsection{Estimating Support For Connectivity Kernel}
The support for the connectivity kernel can be inferred by studying the correlation between consecutive observations of the neural field. 
\begin{itemize}
	\item it is difficult to tell what correlations are from the cross-talk due the the sensor kernel
	\item it is difficult because of the nonlinear function
	\item 
\end{itemize}

@@

\subsection{State-Space Model}
The state-space model is given by
